Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-19 R/CONUS_AOD.Rmd
Added some maps for the AOD CONUS paper.

>>>>

## Maps of new predictions

### Median MSE day

```{r pred.map.median.mse, echo = F}
pred.map(
    tar_read(T.median.mse.map.data)$pred, tar_read(pred_grid),
    bg.sf = get_conus(), color.scale.name = "AOD",
    limits = list(lon = c(-107, Inf), lat = c(-Inf, 37)),
    quantile.cap = .99)
```

This map shows a tile on `r tar_read(T.median.mse.map.data)$date`.

### Baltimore

```{r pred.map.balitmore, echo = F}
pred.map(
    tar_read(T.baltimore.map.data), tar_read(pred_grid),
    bg.sf = get_conus(), color.scale.name = "AOD")
```
